Lynott et al. (2014) - Potential error in statistics reporting

### 2017-11-10 manuscript.Rmd
Made the text box an actual box, introducing a bunch of LaTeX packages in the head

@@

## Box 1: Calculating an equivalence test in R

If you want to calculate an equivalence test based on summary statistics, you can use the "TOSTER" package in the open-source programming language R. Using TOSTER requires very little experience with R, or programming in general. Below are the few simple steps required to calculate an equivalence test with TOSTER.

1. Download, install, and open R.
2. Run `install.packages("TOSTER")` in the console.
3. Run `library(TOSTER)` in the console.
4. The example below reproduces the result of example 1 in R. The parameters of the test are defined inside the parentheses, and you can run `?TOSTtwo` in the console to get information about them. Simply copy the example to the console, replace the values with the corresponding values of your own study, and run the code. Results and a plot will automatically be printed.
```{r eval=FALSE, echo=TRUE, tidy=TRUE, tidy.opts=list(width.cutoff=60)} 
TOSTtwo(m1  = 4.7857, m2  = 4.6569,sd1 = 1.0897, sd2 = 1.1895, n1 = 49, n2 = 51, low_eqbound_d = -0.6401696, high_eqbound_d = 0.6401696, alpha = 0.05, var.equal = FALSE)
```

5. The example above uses the `TOSTtwo()` function in the TOSTER package which calculates an equivalence test for an independent samples t-test. If you need to calculate TOST for a different type of test (e.g. a correlation), you can find documentation for `TOSTr()` and other functions of the TOSTER package by going to https://cran.r-project.org/web/packages/TOSTER/TOSTER.pdf in your web browser.

>>>>

header-includes:
  - \usepackage{float}
  - \usepackage{framed}
  - \usepackage{caption}
  - \usepackage{setspace}
  - \captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
  - \newfloat{textbox}{thp}{lop}
  - \floatname{textbox}{Box}

@@

\begin{textbox}
\caption{Calculating an equivalence test in R}
\begin{framed}
{
\small
\setstretch{1}
If you want to calculate an equivalence test based on summary statistics, you can use the ``TOSTER'' package in the open-source programming language R. Using TOSTER requires very little experience with R, or programming in general. Below are the few simple steps required to calculate an equivalence test with TOSTER. 
\begin{enumerate}
\raggedright
  \setlength{\parskip}{1pt}
\item Download, install, and open R.
\item Run \verb!install.packages("TOSTER")! in the console.
\item Run \verb!library(TOSTER)! in the console.
\item The example below reproduces the result of example 1 in R. The parameters of the test are defined inside the parentheses, and you can run \verb!?TOSTtwo! in the console to get information about them. Simply copy the example to the console, replace the values with the corresponding values of your own study, and run the code. Results and a plot will automatically be printed.
\begin{verbatim}
TOSTtwo(m1  = 4.7857, 
        m2  = 4.6569,
        sd1 = 1.0897, 
        sd2 = 1.1895, 
        n1 = 49, 
        n2 = 51, 
        low_eqbound_d = -0.6401696, 
        high_eqbound_d = 0.6401696, 
        alpha = 0.05, 
        var.equal = FALSE)
\end{verbatim}
\item The example above uses the \verb!TOSTtwo()! function in the TOSTER package which calculates an equivalence test for an independent samples t-test. If you need to calculate TOST for a different type of test (e.g. a correlation), you can find documentation for \verb!TOSTr()! and other functions of the TOSTER package by going to {\sffamily \url{https://cran.r-project.org/web/packages/TOSTER/TOSTER.pdf}} in your web browser. 
\end{enumerate}}
\end{framed} 
\end{textbox}
